\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-11 WOOT/Files/experiment.tex
Update comments

For the purpose evaluating effectiveness of \tool, we conduct experiments in three modes on devices with USB Type-C interface.

>>>>

\shuqing{Experiment for devices and case study needed.}
For the purpose evaluating effectiveness of \tool, we conduct experiments in three modes on devices with USB Type-C interface.
